|

### 2023-06-27 manuscript/manuscript_1.0.Rmd
New word file for Daniel to comment

---
title: |
  The role of learning in status signalling: a modeling approach
author:
- Andrés E. Quiñones:
    email: "andresqp@gmail.com"
    institute: [andes, unine]
    correspondence: true
- Redouan Bshary:
    institute: unine
- C. Daniel Cadena:
    institute: andes
institute:
- andes: Laboratorio de Biología Evolutiva de Vertebrados, Departamento  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia
- unine: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  # word_document: default
  pdf_document:
    latex_engine: xelatex # default  #
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
fig_caption: yes
fontsize: 12pt
header-includes: |
  ```{=latex}
    \usepackage{float}
    \usepackage{unicode-math}
    \usepackage{setspace}\doublespacing
    \usepackage[backref=page]{hyperref}
    \linespread{2}
    \usepackage{lineno}
    \linenumbers
    \floatplacement{figure}{H}
    \newcommand{\beginsupplement}{ \setcounter{table}{0}         \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  ```
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: |
  Adaptive behavioural responses often depend on qualities of the interacting
  partner of an individual. For example, when competing for resources, an individual
  might be better off escalating fights with individuals of lower quality, while
  restraining  from fighting individuals of higher quality. Communication systems
  involving signals of quality allow individuals to reduce uncertainty regarding the
  fighting ability of their partners and make more adaptive behavioral decisions. 
  However, dishonest individuals can destabilize such communications systems. 
  One open question is whether cognitive mechanisms, such as learning, 
  can maintain the honesty of signals, thus, favoring their evolutionary 
  stability. Here we present evolutionary simulations, where individuals 
  can produce a signal proportional to their quality; and learn along their
  lifetime the best response to the signal emitted by their peers. Our simulations
  replicate previous results where the handicap principle mediates the evolution 
  of signals. As in traditional models without learning, in our simulations 
  learning on the receiver side can mediate the evolution of signals
  of quality on the sender side. When the cost of the signal is proportional to the
  quality of the sender populations are only composed of honest signalers. When the
  cost is not proportional to the quality of the signaler tranditional models 
  predict the absense of a signal, in contrast learning facilitates the 
  evolution of a polymorphim where population is composed of both honest and 
  dishonest signalers. We argue that learning can be a general cognitive mechanism 
  role wide range of communication systems and more generally
  behavioral responses."
---

>>>>

---
title: |
  The role of learning in status signalling: a modeling approach
author:
- Andrés E. Quiñones:
    email: "andresqp@gmail.com"
    institute: [andes, unine]
    correspondence: true
- Redouan Bshary:
    institute: unine
- C. Daniel Cadena:
    institute: andes
institute:
- andes: Laboratorio de Biología Evolutiva de Vertebrados, Departamento  de Ciencias Biológicas, Universidad de los Andes, Bogotá, Colombia
- unine: Institute of Biology, University of Neuchâtel, Neuchâtel, Switzerland
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  # word_document: default
  pdf_document:
    latex_engine: xelatex # default  #
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
fig_caption: yes
fontsize: 12pt
header-includes: |
  ```{=latex}
    \usepackage{float}
    \usepackage{unicode-math}
    \usepackage{setspace}\doublespacing
    \usepackage[backref=page]{hyperref}
    \linespread{2}
    \usepackage{lineno}
    \linenumbers
    \floatplacement{figure}{H}
    \newcommand{\beginsupplement}{ \setcounter{table}{0}         \renewcommand{\thetable}{S\arabic{table}}\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
  ```
keep_tex: yes
keywords: My keywords
linespread: 2
bibliography: ../SocialMorphCue.bib
spacing: double
style: C:\Users\andre\Zotero\styles\elife.csl
abstract: |
  Adaptive behavioural responses often depend on qualities of the interacting
  partner of an individual. For example, when competing for resources, an individual
  might be better off escalating fights with individuals of lower quality, while
  restraining  from fighting individuals of higher quality. Communication systems
  involving signals of quality allow individuals to reduce uncertainty regarding the
  fighting ability of their partners and make more adaptive behavioral decisions. 
  However, dishonest individuals can destabilize such communications systems. 
  One open question is whether cognitive mechanisms, such as learning, 
  can maintain the honesty of signals, thus, favoring their evolutionary 
  stability. Here we present evolutionary simulations, where individuals 
  can produce a signal proportional to their quality; and learn along their
  lifetime the best response to the signal emitted by their peers. Our simulations
  replicate previous results where the handicap principle mediates the evolution 
  of signals. As in traditional models without learning, in our simulations 
  learning on the receiver side can mediate the evolution of signals
  of quality on the sender side. When the cost of the signal is proportional to the
  quality of the sender populations are only composed of honest signalers. When the
  cost is not proportional to the quality of the signaler tranditional models 
  predict the absense of a signal, in contrast learning facilitates the 
  evolution of a polymorphim where population is composed of both honest and 
  dishonest signalers. We argue that learning can be a general cognitive mechanism 
  role wide range of communication systems and more generally
  behavioral responses."
---
